Measurement Bias from Address Aliasing

### 2016-01-09 paper.tex
Compressed the intro.

\section{Introduction}
Accurately measuring the performance of computer programs is important in order to evaluate new algorithms, or compare different implementations.
A key challenge for performance analysts and systems researchers is handling \emph{measurement bias}.
Changes to external factors of the system, such as link ordering or the contents of environment variables, has been shown to have potentially significant impacts on performance in real applications~\cite{Mytkowicz:2009:WrongData}.
The underlying explanation is likely that this changes memory addresses of code or data, which in turn interacts with various low level hardware buffers at runtime.
Because of the complexity of modern processors, it is often hard or even impossible to predict exactly how changes to for example system environment variables ultimately affect program execution.

>>>>

\section{Introduction}
Accurately measuring the performance of computer programs is important in order to evaluate new algorithms, or compare different implementations.
A key challenge for performance analysts and systems researchers is handling \emph{measurement bias}.
Changes to external factors of the system, such as link ordering or the contents of environment variables, has been shown to have potentially significant impacts on performance in real applications~\cite{Mytkowicz:2009:WrongData}.
The underlying explanation is that this changes memory addresses of code or data, which in turn interacts with various low level hardware buffers at runtime.
Because of the complexity of modern processors, it is often hard or even impossible to predict exactly how changes to for example system environment variables ultimately affect program execution.
